### 2021-02-11 cover_letter.tex
more precise wording

  \item Following the suggestion of Reviewer 1, we added a simple example program
in the root of the repository ({\tt example.cpp}), and added a link to it from the
ensmallen documentation at \url{https://ensmallen.org/docs.html}.
The example program is indeed very useful for newcomers.
\end{itemize}

>>>>

  \item Following the suggestion of Reviewer 1, we added a simple example program
in the root of the repository ({\tt example.cpp}), and added a link to it from the
online documentation at \url{https://ensmallen.org/docs.html}.
The example program is indeed very useful for newcomers.
\end{itemize}
